\clearpage
\pagenumbering{Roman}
\setcounter{page}{5}
%you have to add the bibliography items in mijnbibliografie.bib. Most editors offer a menu for this. Also, in google scholar (settings, advanced) you can turn on @get bibtex citation@, this gives you a text to copy in the bibfile.
\chapter*{Bibliography}
\addcontentsline{toc}{chapter}{Bibliography}
\textbf{Aguiar, M., \& Amador, M. (2019).} A contraction for sovereign debt models. Journal of Economic Theory, 183, 842–875. \url{https://doi.org/10.1016/j.jet.2019.08.005}\\

\textbf{Aguiar, M., \& Gopinath, G. (2006).} Defaultable debt, interest rates and the current account. Journal of International Economics, 69(1), 64–83.\url{https://doi.org/10.1016/j.jinteco.2005.05.005}\\

\textbf{Alfaro, L., \& Kanczuk, F. (2007).} Optimal Reserve Management and Sovereign Debt (SSRN Scholarly Paper ID 996077). Social Science Research Network. \url{https://doi.org/10.2139/ssrn.996077}\\

\textbf{Arellano, C. (2008).} Default Risk and Income Fluctuations in Emerging Economies. American Economic Review, 98(3), 690–712. \url{https://doi.org/10.1257/aer.98.3.690}\\

\textbf{Arellano, C., \& Ramanarayanan, A. (2012).} Default and the Maturity Structure in Sovereign Bonds. Journal of Political Economy, 120(2), 187–232. \url{https://doi.org/10.1086/666589}\\

\textbf{Auclert, A., \& Rognlie, M. (2016).} Unique equilibrium in the Eaton–Gersovitz model of sovereign debt. Journal of Monetary Economics, 84, 134–146. \url{https://doi.org/10.1016/j.jmoneco.2016.10.013}\\

\textbf{Ayres, J., Navarro, G., Nicolini, J. P., \& Teles, P. (2018).} Sovereign default: The role of expectations. Journal of Economic Theory, 175, 803–812. \url{https://doi.org/10.1016/j.jet.2018.02.006}\\

\textbf{Bellman, R. E. (1954).} The Theory of Dynamic Programming. RAND Corporation. \url{https://www.rand.org/pubs/papers/P550.html}\\

\textbf{Bénassy-Quéré, A., Boot, A., Fatás, A., Fratzscher, M., Fuest, C., Giavazzi, F., Marimon, R., Martin, P., Pisani-Ferry, J., Reichlin, L., Schoenmaker, D., Teles, P., \& Mauro, B. W. di. (2020a).} A proposal for a Covid Credit Line. VoxEU.Org. \url{https://voxeu.org/article/proposal-covid-credit-line}\\
\clearpage
\textbf{Bénassy-Quéré, A., Corsetti, G., Fatás, A., Felbermayr, G., Fratzscher, M., Fuest, C., Giavazzi, F., Marimon, R., Martin, P., Pisani-Ferry, J., Reichlin, L., Rey, H., Schularick, M., Südekum, J., Teles, P., Véron, N., \& Mauro, B. W. di. (2020b).} COVID-19 economic crisis: Europe needs more than one instrument. VoxEU.Org. \url{https://voxeu.org/article/covid-19-economic-crisis-europe-needs-more-one-instrument}\\

\textbf{Botta, A., Caverzasi, E., \& Russo, A. (2020).} Fighting the COVID-19 emergency and re-launching the European economy: Debt monetization and recovery bonds. In Greenwich Papers in Political Economy (No. 27605; Greenwich Papers in Political Economy). University of Greenwich, Greenwich Political Economy Research Centre. \url{https://ideas.repec.org/p/gpe/wpaper/27605.html}\\

\textbf{Boz, E. (2011).} Sovereign default, private sector creditors, and the IFIs. Journal of International Economics, 83(1), 70–82. \url{https://doi.org/10.1016/j.jinteco.2010.10.001}\\

\textbf{Brunnermeier, M. K., Langfield, S., Pagano, M., Reis, R., Nieuwerburgh, S. V., \& Vayanos, D. (2016).} ESBies: Safety in the tranches. In ESRB Working Paper Series (No. 21; ESRB Working Paper Series). European Systemic Risk Board. \url{https://ideas.repec.org/p/srk/srkwps/201621.html}\\

\textbf{Chatterjee, S., \& Eyigungor, B. (2012).} Maturity, Indebtedness, and Default Risk. American Economic Review, 102(6), 2674–2699. \url{https://doi.org/10.1257/aer.102.6.2674}\\

\textbf{Chatterjee, S., \& Eyigungor, B. (2015).} A Seniority Arrangement for Sovereign Debt. The American Economic Review, 105(12), 3740–3765. JSTOR.\url{https://www.jstor.org/stable/43821391?seq=1#metadata_info_tab_contents}\\

\textbf{Claessens, S., Mody, A., \& Vallée, S. (2012).} Paths to Eurobonds (SSRN Scholarly Paper ID 2169717). Social Science Research Network. \url{https://papers.ssrn.com/abstract=2169717}\\

\textbf{Collignon, S. (2011).} Eurobonds: The Financial Equivalent of the Single Currency. \url{https://www.europarl.europa.eu/document/activities/cont/201103/20110316AT}\linebreak\url{T15716/20110316ATT15716EN.pdf}\\

\textbf{Cuadra, G., \& Sapriza, H. (2008).} Sovereign default, interest rates and political uncertainty in emerging markets. Journal of International Economics, 76(1), 78–88. \url{https://doi.org/10.1016/j.jinteco.2008.05.001}\\

\textbf{De La Dehesa, G. (2011).} Eurobonds: Concepts and Implications. \url{https://www.europarl.europa.eu/document/activities/cont/201103/20110}\linebreak\url{316ATT15714/20110316ATT15714EN.pdf}\\

\textbf{Delpla, J., \& Von Weizsäcker, J. (2010).} The Blue Bond Proposal | Bruegel. \url{https://www.bruegel.org/2010/05/the-blue-bond-proposal/}\\

\textbf{Doluca, H., Hübner, M., Rumpf, D., \& Weigert, B. (2013).} The European Redemption Pact. \url{https://www.cairn.info/revue-de-l-ofce-2013-1-page-341.htm}\\

\textbf{Eaton, J., \& Gersovitz, M. (1981).} Debt with Potential Repudiation: Theoretical and Empirical Analysis. The Review of Economic Studies, 48(2), 289–309. JSTOR. \url{https://doi.org/10.2307/2296886}\\

\textbf{Eijffinger, S. C. W. (2011).} Eurobonds – Concepts and Implications. \url{https://www.europarl.europa.eu/document/activities/cont/201103/20110316ATT15714/2011}\linebreak\url{0316ATT15714EN.pdf}\\

\textbf{ESRB. (2018).} Sovereign bond-backed securities: A feasibility study. \url{https://www.esrb.europa.eu/pub/task_force_safe_assets/shared/pdf/esrb.report290118_sbbs_volume_I_mainfindings.en.pdf}\\

\textbf{Eurostat. (2020a)}. Exchange rates and interest rates: EMU convergence criterion series - annual. [Data file]. Retrieved from \url{https://ec.europa.eu/eurostat/web/exchange-and-interest-rates/data/database}\\ 

\textbf{Eurostat. (2020b)} Government statistics: General government gross debt. [Data file]. Retrieved from \url{https://ec.europa.eu/eurostat/web/government-finance-statistics/data/main-tables}\\

\textbf{European Commission. (1993).} Growth, Competitiveness, Employment - The Challenges and Ways Forward into the 21st Century - White Paper. Publications Office of the European Union. \url{http://op.europa.eu/en/publication-detail/-/publication/4e}\linebreak\url{6ecfb6-471e-4108-9c7d-90cb1c3096af/language-en}\\

\textbf{European Commission. (2019).} Vade Mecum on the Stability and Growth Pact – 2019 Edition. European Commission - European Commission. \url{https://ec.europa.eu/info/publications/vade-mecum-stability-and-growth-pact-2019-edition\_en}\\

\textbf{Fink, F., \& Scholl, A. (2016).} A quantitative model of sovereign debt, bailouts and conditionality. Journal of International Economics, 98, 176–190. \url{https://doi.org/10.1016/j.jinteco.2015.09.007}\\

\textbf{Galí, J., López-Salido, J. D., \& Vallés, J. (2005).} Understanding the Effects of Government Spending on Consumption (Working Paper No. 11578; Working Paper Series). National Bureau of Economic Research. \url{https://doi.org/10.3386/w11578}\\

\textbf{Gelos, R. G., Sahay, R., \& Sandleris, G. (2004).} Sovereign Borrowing by Developing Countries: What Determines Market Access? International Monetary Fund, IMF Working Papers. \url{https://www.imf.org/en/Publications/WP/Issues/2016/12/31/Sovereign-Borrowing-by-Developing-Countries-What-Determines-Market-Ac-}\linebreak\url{cess-17560}\\
\clearpage
\textbf{Gelos, R. G., Sahay, R., \& Sandleris, G. (2011).} Sovereign borrowing by developing countries: What determines market access? Journal of International Economics, 83(2), 243–254. \url{https://doi.org/10.1016/j.jinteco.2010.11.007}\\

\textbf{Guscina, A., Malik, S., \& Papaioannou, M. G. (2017).} Assessing Loss of Market Access: Conceptual and Operational Issues (SSRN Scholarly Paper ID 3079570). Social Science Research Network. \url{https://papers.ssrn.com/abstract=3079570}\\

\textbf{Haferkamp, W. (1974).} Summary of the statement [on balance of payment loans] by Mr. Wilhelm Haferkamp, Vice-President of the EEC Commission, to the European Parliament. Strasbourg, 18 October 1974 [EU Speech]. \url{http://aei.pitt.edu/13009/}\\

\textbf{Hatchondo, J. C., \& Martinez, L. (2009).} Long-duration bonds and sovereign defaults. Journal of International Economics, 79(1), 117–125. \url{https://doi.org/10.1016/j.jinteco.2009.07.002}\\

\textbf{Hatchondo, J. C., Martinez, L., \& Onder, Y. K. (2017).} Non-defaultable debt and sovereign risk. Journal of International Economics, 105, 217–229. \url{https://doi.org/10.1016/j.jinteco.2017.01.008}\\

\textbf{Hatchondo, J. C., Martinez, L., \& Sapriza, H. (2010).} Quantitative properties of sovereign default models: Solution methods matter. Review of Economic Dynamics, 13(4), 919–933. \url{https://doi.org/10.1016/j.red.2010.03.001}\\

\textbf{Juncker, J.-C., \& Tremonti, G. (2010, December 5).} E-bonds would end the crisis. Financial Times. \url{http://www.astrid-online.it/static/upload/protected/Junc/Juncker-Tremonti.pdf}\\

\textbf{Juncker, J.-C., Tusk, D., Dijsselbloem, J., Draghi, M., \& Schulz, M. (2015).} The Five President’s Report: Completing Europe’s Economic and Monetary Union. 24. \url{https://ec.europa.eu/commission/sites/beta-political/files/5-presidents-}\linebreak\url{report_en.pdf}\\

\textbf{Lane, P. R. (2012).} The European Sovereign Debt Crisis. Journal of Economic Perspectives, 26(3), 49–68. \url{https://doi.org/10.1257/jep.26.3.49}\\

\textbf{Member States of the European Union. (2007).} Treaty on the Functioning of the European Union. \url{https://eur-lex.europa.eu/legal-content/EN/TXT/?uri=CELEX%3A12012E%2FTXT}\\

\textbf{Mendoza, E. G., \& Yue, V. Z. (2012).} A General Equilibrium Model of Sovereign Default and Business Cycles. The Quarterly Journal of Economics, 127(2), 889–946. \url{https://doi.org/10.1093/qje/qjs009}\\

\textbf{Moesen, W., \& De Grauwe, P. (2009).} Gains for All: A proposal for a common Eurobond. CEPS. \url{https://www.ceps.eu/ceps-publications/gains-all-proposal-common-eurobond/}\\

\textbf{Önder, Y. K. (2016).} Does Multiplicity of Equilibria Arise in the Eaton-Gersovitz Model of Sovereign
Default? In Working Papers (No. 1610; Working Papers). Research and Monetary Policy Department, Central Bank of the Republic of Turkey. \url{https://ideas.repec.org/p/tcb/wpaper/1610.html}\\

\textbf{Önder, Y. K., \& Sunel, E. (2020).} The role of risk aversion in a sovereign default model of polarization and political instability. Review of Economic Dynamics, 35, 123–132. \url{https://doi.org/10.1016/j.red.2019.05.003}\\

\textbf{Philippon, T., \& Hellwig, C. (2011).} Eurobills, not Eurobonds. VoxEU.Org. \url{https://voxeu.org/article/eurobills-not-euro-bonds}\\

\textbf{Reinhart, C., \& Rogoff, K. (2015).} Financial and Sovereign Debt Crises: Some Lessons Learned and Those Forgotten. Journal of Banking and Financial Economics, 14, 38–50. \url{https://doi.org/10.7172/2353-6845.jbfe.2015.2.1}\\

\textbf{Smets, F., \& Wouters, R. (2002).} An Estimated Stochastic Dynamic General Equilibrium Model of the Euro Area. SSRN Electronic Journal, 1. \url{https://doi.org/10.2139/ssrn.1691984}\\

\textbf{Uribe, M., \& Schmitt-Grohé, S. (2017).} Open Economy Macroeconomics (1st edition). Princeton University Press.\\

\textbf{Wyplosz, C. (2011).} Eurobonds: Concepts and Applications. \url{http://intranet.graduateinstitute.ch/files/live/sites/intranet/files/users/admin_students/wyplosz/Reports/ECON%2011.1.pdf}\\

\textbf{Yue, V. Z. (2010).} Sovereign default and debt renegotiation. Journal of International Economics, 80(2), 176–187. \url{https://doi.org/10.1016/j.jinteco.2009.11.004}\\